DOM Review Summary

### 2024-03-14 Analysis/ReviewSummary/ReviewSummary.qmd

library(tidyverse)
library(readxl)
library(knitr)
```

@@

studyDetails_clean <- review_StudyDetails |>
  filter(Status == "Complete")
```

@@

studyDetails_clean |>
  summarise(Articles = n(), .by = "Journal") |>
  mutate(Journal = case_when(Articles == 1 ~ "Other",
                             .default = Journal)) |>
  summarise(Articles = sum(Articles), .by = "Journal") |> 
  arrange(-Articles) |>
  kable()
```

@@

@@

## Authorship category trends

## Review coverage

>>>>

library(tidyverse)
library(readxl)
library(knitr)
library(reactable)
```

@@

studyDetails_clean <- review_StudyDetails |>
  filter(Status == "Complete")  |>
  mutate(YearStrata = case_when(Year %in% 2000:2005 ~ "2000-2005",
                                Year %in% 2006:2010 ~ "2006-2010",
                                Year %in% 2011:2015 ~ "2011-2015",
                                Year %in% 2016:2020 ~ "2016-2020",
                                Year %in% 2021:2023 ~ "2021-2023"))
```

## Year coverage

```{r StudyDetails_years}
studyDetails_clean |>
  filter(!is.na(YearStrata)) |>
  mutate(YearStrata = fct(YearStrata,
                          levels = c("2000-2005", "2006-2010",
                                     "2011-2015", "2016-2020",
                                     "2021-2023"))) |>
  summarise(Articles = n(), .by = YearStrata) |>

  ggplot() +
  geom_col(aes(x = YearStrata, y = Articles), fill = "darkslategrey") +
  labs(title = "Number of articles by year strata",
       x = "Year Strata", y = "Number of articles")
```

@@

journalsTable <- studyDetails_clean |>
  summarise(Articles = n(), .by = "Journal") |>
  arrange(-Articles, Journal) 
```

`{r} nrow(journalsTable)` unique journals are represented in the sample - `{r} nrow(filter(journalsTable, Articles >1))` journals have more than one article.

```{r StudyDetails_journalsTable}
#| echo: false
reactable(journalsTable, defaultPageSize = 8)
```

@@

```{r StudyDetails_countries}
#| echo: false

countriesTable <- studyDetails_clean |>
  summarise(Articles = n(), .by = "FirstAuthor") |>
  arrange(-Articles)
```

Counting by the location of the first author's institution, `{r} nrow(countriesTable` countries are represented in the sample. A strong majority of articles were published by first authors based in the United States of America.

```{r StudyDetails_countriesTable}
#| echo: false

reactable(countriesTable, defaultPageSize = 8)
```

@@

```{r StudyDetails_Categories}
#| echo: false

authorCategories_overall <- studyDetails_clean |>
  separate_rows(AuthorCategories, sep = ", ") |> 
  summarise(Articles = n(),
            Proportion = n()/nrow(studyDetails_clean),
            .by = AuthorCategories) |>
  mutate(Proportion = round(Proportion, 2)) |>
  rename(Category = AuthorCategories) |>
  arrange(-Proportion)
```

The most frequent category of authorship was academic, with `{r} max(authorCategories_overall)`% of articles having at least one author from an academic institution.

```{r StudyDetails_CategoriesTable}
#| echo: false

kable(authorCategories_overall)
```

There is limited discernible change in authorship categories over time.

```{r StudyDetails_authorshipTrend}
#| echo: false
#| warning: false

studyDetails_clean |>
  filter(!is.na(YearStrata)) |>
  mutate(StrataArticles = n(), .by = YearStrata) |>
  separate_rows(AuthorCategories, sep = ", ") |> 
  summarise(Articles = n(),
            .by = c(AuthorCategories, YearStrata, StrataArticles)) |>
  mutate(Proportion = Articles/StrataArticles) |>
  mutate(YearStrata = fct(YearStrata,
                          levels = c("2000-2005", "2006-2010",
                                     "2011-2015", "2016-2020",
                                     "2021-2023")),
         AuthorCategories = fct(AuthorCategories,
                                levels = c("Academic", "Government",
                                           "NGO", "Private"))) |>
  complete(AuthorCategories, YearStrata) |>

  ggplot(aes(x = YearStrata, 
                 y = Proportion, 
                 fill = AuthorCategories)) +
  geom_col(position = "dodge") +
  labs(title = "Authorship trends over time",
       x = "Year of publication",
       y = "Proportion of Articles") +
  scale_fill_manual("Authorship category",
                    values = c("darkslategrey", "darkorchid3",
                               "cyan3", "goldenrod1"))
```

##
